Active Learning with Sentence Error Classification in Machine Translation

### 2020-11-12 Paper/workflow.tex
added basic info on error classification

\subsection{Error Classification}
\label{sec:method-error}

>>>>

\subsection{Error Classification}
\label{sec:method-error}
The following section outlines the error classification process for identifying errors 
in the machine translated outputs from German/Gujarati to English. Specifically, we are 
interested in the three main error types: 
    (1) Grammar: mis-selection and mis-ordering errors including contraction, verbs, 
                agreement; 
    (2) Lexis: errors like omission of words, addition of extra words (that are not needed), 
                and un-translated outputs; and 
    (3) Orthography: errors that deal with punctuation, improper capitalization, spelling 
                mistakes, etc. 
Additionally, we also attempted at classification of semantic errors (wrong choice, collocational errors and idoms)
and discourse errors (style, variety, etc.).
